%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\linespread{1.1}
\begin{document}
\header{boris}{pfahringer}
       {computer science / math}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    7 Sutton Cres
    Hamilton 3216
    New Zealand
    ~
    \href{mailto:bpnzltd@gmail.com}{bpnzltd@gmail.com}
    +64 7 856 9414
  \section{languages}
    bilingual english/german
  \section{programming}
    Java, Python, C
    HTML, JS, CSS
    {\color{red} $\varheartsuit$} Haskell
\end{aside}

\section{profile}

I'm a computer science and mathematics student at the University of Waikato.
My direction academically is towards formal methods, algorithms and networks.
I'm looking to develop as a programmer and to learn as much about developing
sound robust software, and esoteric maths as I can.

I have been involved with the \href{http://www.nzoi.org.nz/}
{New Zealand Olympiad in Informatics}, competing twice at the International
Olympiad in Informatics in Sofia, Bulgaria and Waterloo, Canada, being
awarded a bronze medal at both. Since then I have volunteered annually at the
NZOI's summer training and selection camp and helped local candidates in
their contest preparations.

Outside of Computer Science, I enjoy playing soccer at the Unicol Football
Club for the men's Federation 1 team. I also regularly practise pilates and
ballroom dancing.

\section{education}

\begin{entrylist}
  \entry
    {since 2010}
    {BCMS \normalfont{candidate \footnotesize{(GPA: 9.0)}}}
    {Waikato University}
    {Majoring in Computer Science and Mathematics}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {since 2011}
    {Part-time Software Developer.}
    {Anvil Labs, Hamilton}
    {Construction and maintenance of promotional websites. (Python + HTML5)}

  \entry
    {2011--2012}
    {Research Scholarship}
    {University of Waikato, Hamilton}
    {Develop a compiler and IDE for the research language
    \href{http://www.cs.waikato.ac.nz/research/jstar/}{JStar}.
    Developed using Java and Xtext, currently being used to teach
    \href{http://papers.waikato.ac.nz/subjects/COMP/COMP553}
    {Extremely Parallel Programming} at Waikato.}

  \entry
    {07--11 2011}
    {Seasonal Assistant}
    {University of Waikato, Hamilton}
    {Marking assignments, tests, and tutoring students during
    practical lab sessions in the paper
    \href{http://papers.waikato.ac.nz/subjects/COMP/COMP235}
    {Logic and Computation}.}

  \entry
    {08--10 2010}
    {Research Programmer}
    {University of Waikato, Hamilton}
    {Development on
    \href{http://www.wand.net.nz/scamper}{scamper},
    an open source network testing and mapping tool. (C)}
\end{entrylist}

\section{honours}
\begin{entrylist}
  \titleentry
    {2011}
    {Millennium Prize in Mathematics}
    {University of Waikato}

  \titleentry
    {2011}
    {Prize for Excellence}
    {UoW Alumni Association}

  \titleentry
    {2009--2011}
    {Summer Research Scholarship}
    {University of Waikato}

  \titleentry
    {2010--2011}
    {Dean's Award for Excellence}
    {University of Waikato}

  \titleentry
    {2010}
    {Von Neumann Prize in Mathematics}
    {University of Waikato}

  \titleentry
    {2009--2010}
    {Two Bronze Medals}
    {International Olympiad in Informatics}

  \titleentry
    {2009}
    {Computer Science Entrance Scholarship}
    {University of Waikato}

  \titleentry
    {2009}
    {Outstanding Scholar Award}
    {New Zealand Qualifications Authority}
\end{entrylist}

\section{referees}

\referee
  {Margot Phillips}
  {Executive Director, NZOI Inc.}
  {email: \href{mailto:margot.phillips@gmail.com}{margot.phillips@gmail.com}}

\referee
  {Mark Utting}
  {Associate Professor, University of Waikato}
  {phone: +64 7 838 4791,
  email: \href{mailto:marku@cs.waikato.ac.nz}{marku@cs.waikato.ac.nz}}

\referee
  {Matthew Luckie}
  {Researcher, CAIDA}
  {email: \href{mailto:mjl@caida.org}{mjl@caida.org}}
\end{document}
